% Cover letter using letter.cls
\documentclass[11pt]{letter} % default is 10 pt
\usepackage{helvetica} % uses helvetica postscript font (download helvetica.sty)
% the following commands control the margins:
\topmargin=-1in    % Make letterhead start about 1 inch from top of page
\textheight=8.5in  % text height can be bigger for a longer letter
\oddsidemargin=0pt % leftmargin is 1 inch
\textwidth=6.5in   % textwidth of 6.5in leaves 1 inch for right margin

\begin{document}


\signature{Udit Manektala}                  % name for signature 
\longindentation=0pt                       % needed to get closing flush left
\let\raggedleft\raggedright                % needed to get date flush left
 
\begin{letter}{Recruiter\\
Yelp} 

\begin{center}
\large\bf UDIT MANEKTALA\\
udit@manektala.com\\
\end{center} 
\vfill % forces letterhead to top of page


 
\opening{Dear Sir/Ma'am} 
 
\noindent I've been a Yelp user for a long time now and have always been very impressed with your product. Yelp is like my dowsing stick for tracking down San Francisco's hidden culinary gems. And for this superpower, I am grateful.

 I'm a developer working with a software-consultancy (ThoughtWorks) for 5-6 years now and I'm looking for other opportunities. Between my work and my personal projects, I have lots of Web Development experience. The prospect of working for your company excites me enough to motivate to me write a Cover Letter in LaTeX. I don't remember the last cover letter I ever wrote. But I digress. 

I would like to apply for the position of Web Developer. But really, I like to think of myself as a software generalist with predominantly web development experience. But I digress. My resume is at udit.manektala.com. I would love to hear from you guys about this opportunity.
 
\closing{Sincerely yours,}
 
 

\end{letter}
 

\end{document}




